Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-01 journal/article.tex
Work in progress

[P38]
* Why: Management needed to show benefits of agile greatly
* Who: A project was selected particularly for the pilot
* Who: It was a project deemed to be plausible for a good end result
* Result: The pilot was successful
* Result: Business was pleased with the result
* Particular: People got false expectations based on the success of the pilot

@@

>>>>

[P38]
* Why: Management needed to show benefits of agile greatly
* Who: A project was selected particularly for the pilot
* Who: It was a project deemed to be plausible for a good end result
* Result: The pilot was successful
* Result: Business was pleased with the result
* Particular: People got false expectations based on the success of the pilot
* Who: The pilot team was an all star team

@@

[P40]
* Amount: 5 projects
* Result: The pilots were successful
* Result: The organization proceeded with wider adopiton

[P43]
* Amount: 8 months of experimenting
* Result: Clear success in projects that used agile
* Result: The organization was ready for full roll-out

[P45]
* Who: Teams by their own interest
* Amount: A number of pilot projects
* Result: There was important findings in applicability and limitations
* Result: Data was gathered, and adjustments were made thereby
* Particular: The pilot gave unrealistic expectations, and the scaling up was more difficult than the pilot projects

[P46]
* Why: To get started
* Amount: 2 pilot projects
* Result: The pilots got done?

[P47]
* Amount: Many areas of the company
* Result: Pilots showed great successs
* Result: Teams showed a strong desire to continue with agile
* Result: Executive management was supportive
